National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs

### 2020-11-20 Manuscript.Rmd

---
title             : "National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs"
shorttitle        : "Longitudinal Wellbeing from Spiritual Beliefs"
author: 
  - name          : "Ben Highland"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Ben's Postal address"
    email         : "benhighland6420@gmail.com"
  - name          : "Everett L. Worthington"
    affiliation   : "2"
    institution   : "Department of Psychology Virginia Commonwealth University"
  - name          : "Don E Davis"
    affiliation   : "3"
    institution   : "Department of Psychology Georgia State University"
  - name          : "Chris G. Sibley"
    affiliation   : "4"
    institution   : "School of Psychology University of Auckland"
  - name          : "Joseph A. Bulbulia"
    affiliation   : "5"
    institution   : "School of Psychology Victoria University"

authornote: |
  1 Wake Forest Medical School 2 Department of Psychology Virginia Commonwealth University 3 Department of Psychology Georgia State University 4 School of Psychology University of Auckland 5 School of Psychology Victoria University

@@

<!-- In spirituality/psychological wellbeing research,subjective in spirituality health research, psychological well-being is typically decomposed into two categories: emotional well-being (i.e., the presence or absence of positive feelings about life) and functional well-being (i.e., psychological and social well-being) [@Keyes2002-bb]. -->

>>>>

---
title             : "National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs"
shorttitle        : "Longitudinal Wellbeing from Spiritual Beliefs"
author: 
  - name          : "Benjamin Highland"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "520 Power Plant Circle Apartment 105 Winston-Salem, NC 27101 USA"
    email         : "benhighland6420@gmail.com"
  - name          : "Everett L. Worthington"
    affiliation   : "2"
    institution   : "Department of Psychology Virginia Commonwealth University"
  - name          : "Don E Davis"
    affiliation   : "3"
    institution   : "Department of Psychology Georgia State University"
  - name          : "Chris G. Sibley"
    affiliation   : "4"
    institution   : "School of Psychology University of Auckland"
  - name          : "Joseph A. Bulbulia"
    affiliation   : "5"
    institution   : "School of Psychology Victoria University"

authornote: |
  1 Wake Forest School of Medicine 2 Department of Psychology Virginia Commonwealth University 3 Department of Psychology Georgia State University 4 School of Psychology University of Auckland 5 School of Psychology Victoria University

@@

<!-- In spirituality/psychological wellbeing research, subjective in spirituality health research, psychological well-being is typically decomposed into two categories: emotional well-being (i.e., the presence or absence of positive feelings about life) and functional well-being (i.e., psychological and social well-being) [@Keyes2002-bb]. -->
